
	%----------------------------------------------------------------------------------------
	%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
	%----------------------------------------------------------------------------------------

	\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
	\usepackage{tikz}
	\usetikzlibrary{tikzmark}
	\usetikzlibrary{calc}
	\usepackage{enumitem}
	\setlist{nosep}
	%----------------------------------------------------------------------------------------

	\begin{document}

	%----------------------------------------------------------------------------------------
	%	TITLE AND CONTACT INFORMATION
	%----------------------------------------------------------------------------------------

	\begin{minipage}[t]{0.365\textwidth} % 38% of the page width for name
		\vspace{-\baselineskip} % Required for vertically aligning minipages
		\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Benjamin}}}}}
		\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Anderson}}}}}
		\vspace{6pt}

		{\huge Electronic Engineer}
	\end{minipage}
	\begin{minipage}[t]{0.365\textwidth} % 38% of the page width for the first row of icons
		\vspace{-\baselineskip} % Required for vertically aligning minipages
		\icon{Phone}{12}{+44 (0)7946 866 875}\\
		\icon{At}{12}{\href{mailto:thebenjaminjanderson@gmail.com}{thebenjaminjanderson@gmail.com}}\\
		\icon{MapMarker}{12}{London}\\	
	\end{minipage}
	\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
		\vspace{-\baselineskip} % Required for vertically aligning minipages

		\icon{Globe}{12}{\href{https://engiebenji.com}{engiebenji.com}}\\
		\icon{Twitter}{12}{\href{https://twitter.com/@engiebenji1999}{@engiebenji1999}}\\
		\icon{Github}{12}{\href{https://github.com/benjaminjanderson}{/benjaminjanderson}}\\
	\end{minipage}

	\vspace{0.5cm}

	%----------------------------------------------------------------------------------------
	%	PROJECTS
	%----------------------------------------------------------------------------------------
	% \begin{tikzpicture}[remember picture,overlay]
	%     \filldraw ($(current page.north east)+(-2.75,-5.7)$) rectangle (current page.south east);
	% \end{tikzpicture}

	\cvsect{Projects}

	\begin{entrylist}
		\QRentry
			{Cube}
			{A handheld device comprising of 6 OLED screens for each face of a cube. This project required design of circuits for battery management and voltage regulation, 3D modelling of the frame, as well as efficient C code to run 6 screens and a 6 DOF sensor off a single ESP32.\\ \texttt{KiCAD}\slashsep\texttt{FreeCAD}\slashsep\texttt{Git}\slashsep\texttt{Blender}}
			{https://engiebenji.com/2022/09/18/CUBE/}
		\QRentry
			{Orthodox}
			{A unique ortholinear keyboard. This project required rapid prototyping of custom keycaps using parametric designs, PCB coils around keyswitches to measure analog keypresses with an LDC chip, as well as a custom driver had to be written to allow for seamless integration of the keyboard with computers \\\texttt{KiCAD}\slashsep\texttt{FreeCAD}\slashsep\texttt{Git}\slashsep\texttt{OpenSCAD}}
			{https://engiebenji.com/2022/09/18/ORTHODOX/}
	\end{entrylist}

	%----------------------------------------------------------------------------------------
	%	EXPERIENCE
	%----------------------------------------------------------------------------------------

	\cvsect{Experience}

	\begin{entrylist}
		\entry
			{2021-2022}
			{RF Test Engineer}
			{\href{https://Curvalux.com}{Curvalux}}
			{	
				\begin{itemize}
					\item[$\bullet$\hspace*{0.5cm}] Used LaTeX to produce clean, formatted reports of data/graphs generated with matplotlib. 
					\item[$\bullet$\hspace*{0.5cm}] Professionally collaborated and documented repositories using gitlab, jira, confluence and slack.
					\item[$\bullet$\hspace*{0.5cm}] Developed python libraries to control rotators, switches, keysight VNAs and beamforming ICs for automating radiation pattern measurements in a custom anechoic chamber.
					\item[$\bullet$\hspace*{0.5cm}] Translated MATLAB algorithms for phase tapering/beam steering a phased array antenna into working code on early prototype hardware.				
				\end{itemize}
			}
		\entry
			{2019-2020}
			{Research \& Development Engineer}
			{\href{https://www.huawei.com/uk/contact-us}{Huawei}}
			{
				\begin{itemize}
					\item[$\bullet$\hspace*{0.5cm}] Analysing reliability of devices with PAM4 / NRZ inspection, shear testing, electroluminescence inspection.
					\item[$\bullet$\hspace*{0.5cm}] Built a standalone program with PyQt to automatically produce failure analysis reports from data gathered by lab technicians, saving countless engineering hours on a repetitive manual task.
					\item[$\bullet$\hspace*{0.5cm}] Developed a python library to communicate with a TEC controller over the serial protocol.
					\item[$\bullet$\hspace*{0.5cm}] Presented weekly meetings to inform senior engineers of device failures and reliability.
				\end{itemize}
			}
			\entry
			{2018-2019}
			{Hardware Engineer}
			{\href{https://avalonrov.wixsite.com/avalonrov}{Avalon}}
			{
				\begin{itemize}
					\item[$\bullet$\hspace*{0.5cm}] Tasked with designing and soldering the power management PCB for an underwater ROV
					\item[$\bullet$\hspace*{0.5cm}] Had meetings with suppliers to discuss partnership/sponserships for the competition.
					\item[$\bullet$\hspace*{0.5cm}] Regularly liaised with engineers from different disciplines to check compatibility.
					\item[$\bullet$\hspace*{0.5cm}] Managed my time effectively to balance commitments to University and Avalon.
				\end{itemize}		
			}
			\entry
			{2018-2019}
			{Design Project}
			{\href{https://www.sheffield.ac.uk/engineering/study/global-engineering-challenge}{Global Engineering Challenge}}
			{
				\begin{itemize}
					\item[$\bullet$\hspace*{0.5cm}] Tasked with diagnosing diseases in Kibera, exploratory research led to designing mobile retina scanners. 
					\item[$\bullet$\hspace*{0.5cm}] Used TensorFlow and an NHS dataset to train a model to determine diseases based on symptoms visible in retinas.
					\item[$\bullet$\hspace*{0.5cm}] Pitched the proof of concept in front of a crowd of 30+ people, receiving questions for 10 minutes.
				\end{itemize}	
			}	
	\end{entrylist}

	%----------------------------------------------------------------------------------------
	%	INTRODUCTION, SKILLS AND TECHNOLOGIES
	%----------------------------------------------------------------------------------------
	\begin{minipage}[t]{0.40\textwidth}% 40% of the page width for the introduction text
		\cvsect{References}

		% \vspace{0.1cm} % Required for vertically aligning minipages
		\halfentry
			{Jason Hanson}
			{Princial RF Engineer}
			{
				\hspace*{0.5cm}jason.hanson@curvalux.co.uk\newline
				\hspace*{0.5cm}+44 (0)7799 036 362\newline
			}
		\halfentry
			{Xiaoli Chu}
			{Ph.D Wireless Communications}
			{
				\hspace*{0.5cm}x.chu@sheffield.ac.uk\newline
				\hspace*{0.5cm}+44 (0)1142 255 903\newline\newline
			}
		\halfentry
			{Lu Zhang}
			{Senior Reliability Engineer}
			{	
				\hspace*{0.5cm}luzhang1@huawei.com\newline
				\hspace*{0.5cm}+44 (0)7881 255 334\newline
			}

		
	\end{minipage}
	\hspace*{0.5cm}
	\begin{minipage}[t]{0.57\textwidth}
		\cvsect{Education}

		% \vspace{0.1cm} % Required for vertically aligning minipages
		\halfentrydate
			{2017-2021}
			{Bachelor of Engineering}
			{University of Sheffield}
			{
				\hspace*{0.5cm}Electronic Engineering:\hfill1st\newline\newline
			}
		\halfentrydate
			{2015-2017}
			{A-Levels}
			{Dunraven}
			{
				\hspace*{0.5cm}Mathematics\hfill B\newline
				\hspace*{0.5cm}Physics\hfill B\newline
				\hspace*{0.5cm}Computing\hfill B\newline
			}
		\halfentrydate
			{2010-2015}
			{GCSEs (11 Qualifications Passed)}
			{Harris Academy}
			{
				\hspace*{0.5cm}Mathematics\hfill A\newline
				\hspace*{0.5cm}Science\hfill A\newline
				\hspace*{0.5cm}English\hfill B\newline
			}
	\end{minipage}%

	\end{document}